---
title: 'Tidy Tuesday: Global SeaFood'
author: "Kesava"
date: 'Report Last Run: `r Sys.time()`'
output:
  html_document:
    code_folding: hide
    theme: flatly
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

Install required packages

```{r message=FALSE, warning=FALSE}
# load required packages
library(tidyverse)
library(tidytuesdayR)
library(janitor)
library(ggstream)
library(scales)
```

# Data

Get this weeks data from Tidy tuesday github.

```{r}
data_tue <- tt_load('2021-10-12', auth = github_pat())
```

There is a lot of information this week I would like to concentrate on Aquaculture production of top 5 countries.

```{r}
# Parameters
caption <- "Tidy Tuesday 10-12-2021 Visualisation by: Kesava Asam \n Data source: OurWorldinData.org"
```

Clean the data and pick the top 5 countries

```{r}
# Clean the aqua culture data
aqua_culture <- 
  data_tue$`aquaculture-farmed-fish-production` %>% 
  clean_names() %>% 
  rename("cultured" = "aquaculture_production_metric_tons") %>% 
  filter(code != "OWID_WRL", !is.na(code))

# Select top 5 countries
countries <- aqua_culture %>%
  filter(year == max(year)) %>%
  arrange(desc(cultured)) %>%
  head(5) %>% 
  pull(entity)
```

\newpage

# Make an area plot!

## Bare back bones

```{r fig.height=10, fig.width=16, message=FALSE}
# Plot the top 5 countries
aqua_plot_1 <- 
  aqua_culture %>% 
  filter(entity %in% countries) %>% 
  mutate(entity = fct_relevel(entity, countries)) %>%
  ggplot(., aes(x=year, fill=entity)) +
  geom_area(aes(y = cultured), 
            alpha = 0.9, linetype = 1, size =0.25, 
            color="grey50", position = "stack") +
  ggdark::dark_theme_void() + 
  theme(legend.position = "left") +
  labs(x = "", y = "", fill = "Country") 

aqua_plot_1
```

## Custom colors

```{r fig.height=10, fig.width=16}
# Add custom colors

## Make custom colors
# color <- c()
# color[order] <- 

## Add to plot
aqua_plot_2 <- 
  aqua_plot_1 + 
  scale_fill_manual(values = colorRampPalette(c("#0286c2", "#00ffea"))(5))

aqua_plot_2
```

## Finalized plot

```{r}
# Add annotations
aqua_plot_final <- 
  aqua_plot_2 + 
  
  ## Million Metric Tons
  annotate("text", x = 2023,  y = 85000000, 
           label = "In 2018, no of \n Million \n Metric Tons \n Cultured", 
           colour = "grey", size =4.5, family = "Georgia") +
  
  geom_segment(aes(x = 2023, xend = 2023, y = 76000000, yend = 64000000),
               arrow = arrow(length = unit(0.15, "cm")), 
               size = 0.5, color = "grey50") +
  
  
  # China
  geom_segment(aes(x = 2018, xend = 2022, y = 65000000, yend = 60000000),
               size = 0.2, color = "#0286C2", linetype = 17) +
  annotate("text", x = 2023,  y = 57000000, 
           label = "China \n 66.1 M", 
           colour = "#0286C2", size =4, family = "Georgia") +
  
  # Indonesia
  geom_segment(aes(x = 2018, xend = 2021.5, y = 22000000, yend = 26000000),
               size = 0.2, color = "#01A4CB", linetype = 17) +
  annotate("text", x = 2023.5,  y = 27000000, 
           label = "Indonesia \n 14.7 M", 
           colour = "#01A4CB", size =4, family = "Georgia") +
  
  
  # India
  geom_segment(aes(x = 2018, xend = 2022, y = 11000000, yend = 15000000),
               size = 0.2, color = "#01C2D5", linetype = 17) +
  annotate("text", x = 2023.5,  y = 16000000, 
           label = "India \n 7 M", 
           colour = "#01C2D5", size =4, family = "Georgia") +
  
   # Vietnam
  geom_segment(aes(x = 2018, xend = 2022, y = 5000000, yend = 6000000),
               size = 0.2, color = "#00E0E0", linetype = 11) +
  annotate("text", x = 2023.5,  y = 7000000, 
           label = "Vietnam \n 4.1 M", 
           colour = "#00E0E0", size =4, family = "Georgia") +
  
  
  # Bangladesh
  geom_segment(aes(x = 2018, xend = 2021, y = 900000, yend = -1000000), 
               size = 0.2, color = "#00FFEA", linetype = 17) +
  annotate("text", x = 2023.5,  y = -3200000, 
           label = "Bangladesh \n 2.4 M", 
           colour = "#00FFEA", size =4, family = "Georgia") +
  
  # Title
  annotate("text", x = 1990,  y = 108000000, 
           label = "Top 5 Countries' aqua culture production over past 50 years", 
           colour = "grey",size =8.0, family = "Georgia") +
  
  # Subtitle
  annotate("text", x = 1990,  y = 102000000, 
           label = "China's 2018 aquaculture production is 4.5X higher than Indonesia", 
           colour = "grey",size =5.0, family = "Times") +
  
  # Caption
  annotate("text", x = 1990,  y = -10000000, 
           label = caption, 
           colour = "grey",size =3.5, family = "Times")
```

\newpage

```{r fig.height=10, fig.width=16}
aqua_plot_final
```

```{r eval=FALSE, include=FALSE}
ggsave("tidy_tuesday_aquaculture_area_plot_1017.jpeg", 
       plot = last_plot(), width = 400, height = 300, 
       units = "mm", dpi = 300)
```

\newpage

# Make a streamplot

This may resemble more of a water body! I wanted to use something that looks like a stream.

```{r fig.height=10, fig.width=16}
aqua_stream_plot <- 
  # Clean up and arrangements
  aqua_culture %>% 
  filter(entity %in% countries) %>% 
  mutate(entity = fct_relevel(entity, countries)) %>% 
  
  ## Plotting
  ggplot(aes(year, cultured, fill=entity)) +
  geom_stream(linetype = 1, size =0.25, 
              color="grey50") +
  scale_y_continuous(label = number_format()) +
  
  ## Custom colors
  scale_fill_manual(values = colorRampPalette(c("#0286c2", "#00ffea"))(5))  +
  ggdark::dark_theme_void() +
  theme(legend.position = "left") +
  labs(fill = "") +
  
  # Annotations
  
  ## Million Metric Tons
  annotate("text", x = 2024,  y = 40000000, 
           label = "In 2018, no of \n Million \n Metric Tons \n Cultured", 
           colour = "grey70", size =4.3, family = "Georgia") +
  
  geom_segment(aes(x = 2024, xend = 2024, y = 34000000, yend = 31000000),
               arrow = arrow(length = unit(0.15, "cm")), 
               size = 0.5, color = "grey70") +
  
  ## China
  geom_segment(aes(x = 2018, xend = 2022, y = 18000000, yend = 20000000),
               size = 0.2, color = "#0286C2") +
  annotate("text", x = 2024,  y = 21000000, 
           label = "China \n 66.1 M", 
           colour = "#0286C2", size =4.3, family = "Georgia") +
  
  ## Indonesia
  geom_segment(aes(x = 2018, xend = 2021.5, y = -24000000, yend = -21000000),
               size = 0.2, color = "#01A4CB") +
  annotate("text", x = 2023.5,  y = -20000000, 
           label = "Indonesia \n 14.7 M", 
           colour = "#01A4CB", size =4.3, family = "Georgia") +
  
  
  # India
  geom_segment(aes(x = 2018, xend = 2022, y = -34000000, yend = -31000000),
               size = 0.2, color = "#01C2D5") +
  annotate("text", x = 2023.5,  y = -30000000, 
           label = "India \n 7 M", 
           colour = "#01C2D5", size =4.3, family = "Georgia")+ 
  
   # Vietnam
  geom_segment(aes(x = 2018, xend = 2022.3, y = -40000000, yend = -39500000),
               size = 0.2, color = "#00E0E0") +
  annotate("text", x = 2024,  y = -38500000, 
           label = "Vietnam \n 4.1 M", 
           colour = "#00E0E0", size =4.3, family = "Georgia") +
  
  
  # Bangladesh
  geom_segment(aes(x = 2018, xend = 2021, y = -42500000, yend = -45000000), 
               size = 0.2, color = "#00FFEA") +
  annotate("text", x = 2024,  y = -46000000, 
           label = "Bangladesh \n 2.4 M", 
           colour = "#00FFEA", size =4.3, family = "Georgia") +
  
  # Title
  annotate("text", x = 1985,  y = 41000000, 
           label = "Top 5 Countries' aquaculture production over past 50 years", 
           colour = "grey",size =9.5, family = "Georgia") +
  
  # Subtitle
  annotate("text", x = 1985,  y = 37500000, 
           label = "China's 2018 aquaculture production is 4.5X higher than Indonesia", 
           colour = "grey",size =6.5, family = "Times") +
  
  # Caption
  annotate("text", x = 1985,  y = -50000000, 
           label = caption, 
           colour = "grey",size =3.5, family = "Times")

aqua_stream_plot
```

## More info

Need to add some more info!

```{r}
# Check the data for more info
aqua_culture %>% 
  filter(entity %in% countries, year %in% c(1960, 1970, 1980, 1990, 2000, 2010, 2018)) %>% 
  group_by(year) %>% 
  mutate(entity = fct_relevel(entity, countries), 
         countries_total = sum(cultured)) %>% 
  select(countries_total)
```

```{r}
# Add the additional info
aqua_stream_plot_final <-
  aqua_stream_plot +
  geom_segment(aes(x = 1960, xend = 1960, y = 0, yend = -20000000),
               size = 0.12, color = "grey60", linetype = 15) +
  annotate("text", x = 1960,  y = -21000000, 
           label = "1960, all 5 countries \n together cultured \n 1.1 M metric tons", 
           colour = "grey90", size =2.6, family = "Arial") +
  
  geom_segment(aes(x = 1970, xend = 1970, y = 0, yend = -22000000),
               size = 0.12, color = "grey60", linetype = 15) +
  annotate("text", x = 1970,  y = -23000000, 
           label = "1970, all 5 countries \n together cultured \n 1.8 M metric tons", 
           colour = "grey90", size =2.6, family = "Arial")+
  
  geom_segment(aes(x = 1980, xend = 1980, y = 0, yend = -24000000),
               size = 0.12, color = "grey60", linetype = 15) +
  annotate("text", x = 1980,  y = -25000000, 
           label = "1980, all 5 countries \n together cultured \n 3.8 M metric tons", 
           colour = "grey90", size =2.6, family = "Arial") +
  
  geom_segment(aes(x = 1990, xend = 1990, y = 0, yend = -26000000),
               size = 0.12, color = "grey60", linetype = 15) +
  annotate("text", x = 1990,  y = -27000000, 
           label = "1990, all 5 countries \n together cultured \n 10.3 M metric tons", 
           colour = "grey90", size =2.6, family = "Arial")+
  
  geom_segment(aes(x = 2000, xend = 2000, y = 0, yend = -28000000),
               size = 0.12, color = "grey60", linetype = 15) +
  annotate("text", x = 2000,  y = -29000000, 
           label = "2000, all 5 countries \n together cultured \n 33.3 M metric tons", 
           colour = "grey90", size =2.6, family = "Arial")+
  
  geom_segment(aes(x = 2010, xend = 2010, y = 0, yend = -39000000),
               size = 0.12, color = "grey60", linetype = 15) +
  annotate("text", x = 2010,  y = -40000000, 
           label = "2010, all 5 countries \n together cultured \n 61.8 M metric tons", 
           colour = "grey90", size =2.6, family = "Arial")+
  
  geom_segment(aes(x = 2018, xend = 2018, y = 0, yend = -48000000),
               size = 0.12, color = "grey60", linetype = 15) +
  annotate("text", x = 2018,  y = -49000000, 
           label = "2018, all 5 countries \n together cultured \n 94.5 M metric tons", 
           colour = "grey90", size =2.6, family = "Arial")
```

## Final Plot

```{r fig.height=10, fig.width=16}
aqua_stream_plot_final
```


```{r eval=FALSE, include=FALSE}
ggsave("tidy_tuesday_aquaculture_stream_plot_1017.jpeg", 
       plot = last_plot(), width = 400, height = 300, 
       units = "mm", dpi = 300)
```

\newpage

# Session

```{r}
sessionInfo()
```

