---
title: 'Tidy Tuesday: Ultra Trail Running'
author: "Kesava"
date: 'Report Last Run: `r Sys.time()`'
output:
  html_document:
    code_folding: hide
    theme: flatly
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set

setwd("~/Documents/tidy_tuesday/2021_10_25_ultra_trail_running")
```

# Packages

Install required packages

```{r message=FALSE, warning=FALSE}
# load required packages
library(tidyverse)
library(tidytuesdayR)
library(janitor)
library(scales)
library(patchwork)
library(countrycode)
```

# Import Data

Get this weeks data from Tidy tuesday github.

```{r}
# read in the data manually

ultra_rankings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-10-26/ultra_rankings.csv')

race <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-10-26/race.csv')

```

# Check data

```{r}
ultra_rankings %>% 
  group_by(runner, nationality) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  head()
```

```{r}
ultra_rankings %>% 
  group_by(nationality) %>% 
  count() %>% 
  arrange(desc(n))
```

```{r}
race %>% summary()
```

# Clean the data

```{r}
race_clean <- 
  race %>% 
  mutate(country = str_replace(country, "^[^,]*, ", "")) %>% 
  filter(participants > 2, participation == "solo", elevation_gain > 0) %>% 
  arrange(desc(elevation_gain)) %>% 
  unite("region", city, country, sep =", ", remove = FALSE )
```

## Join data to get year

```{r}
ultra_race <- 
  inner_join(ultra_rankings, race)
```

# Add continent data

```{r}
runners_cont <- 
  ultra_race %>% 
  mutate(nationality = str_to_upper(nationality)) %>% 
  separate(date, "year", extra = 'drop') %>% 
  group_by(year, nationality) %>%
  count() %>% 
  ungroup() %>% 
  mutate(nationality = recode(nationality, 
                              "SPA" = "ESP"))


runners_cont$continent <- countrycode(sourcevar = runners_cont$nationality,
                            origin = "ioc",
                            destination = "continent")
```

# Check plot

```{r}
runners_cont %>% 
  filter(!is.na(continent)) %>% 
  
  ggplot(aes(x = year, y = n, fill = continent)) + 
  geom_col() +
  facet_wrap(~ factor(continent , levels=c('Africa','Oceania','Asia','Americas', "Europe"))) + 
  scale_y_continuous(breaks = c(100, 1000, 5000, 7000, 10000, 12000)) +
  theme_bw() +
  theme(legend.position = "none")
```

# Make Continent plot

## Set theme and function

```{r}
bcolor <- "#FFF7DF"

theme_set(theme_minimal())

theme_update(
  legend.position = "none", 
  panel.background = element_rect(fill = bcolor, color = NA),
  plot.background = element_rect(fill = bcolor, color = NA),
  panel.grid.major.x = element_blank(), 
  axis.text = element_text(size = 14), 
  axis.title.y = element_text(size = 14)
  # axis.text = element_blank(),
  # axis.title = element_blank()
)

plot_cont <- function(df, var_cont, point_color, bar_color) {
  
  df %>% 
    filter(continent == {{var_cont}}) %>% 
    ggplot(aes(x = year, y = n, fill = continent)) + 
    geom_col() +
    geom_point(aes(size = n), color = "black", alpha = 0.3) +
    geom_point(data=df_labels,aes(size = n), 
             color=point_color) +
    geom_text(data=df_labels, 
              aes(label = nationality), nudge_y = 270,
              check_overlap = T, color = point_color) +
    scale_fill_manual(values = bar_color) +
    scale_y_continuous(limits = c(0, 12000), 
                       breaks = c(100, 1000, 5000, 7000, 10000, 12000)) 
  
}
```

## Asia

```{r}
# Colors
point_color <- "#F193A8"
bar_color <- "#B13A5A"
  
# Labels
df_labels <- 
  runners_cont %>% 
  filter(continent == "Asia", nationality %in% c("JPN", "CHN")) 

asian_plot <- 
  plot_cont(runners_cont, "Asia", point_color, bar_color) +
  labs(x = "", y = "Number of Runners") +
  annotate("text", x = 5,  y = 11000, 
           label = "From Asia", 
           colour = bar_color, size =7.0, family = "Georgia") +
  
  geom_curve(aes(x = 8, y = 1074, xend = 8.6, yend = 4000),
               arrow = arrow(length = unit(0.35,"cm")), 
             color = point_color, size = 0.8, curvature = -0.3) +
  annotate("text", x = 9,  y = 4500, 
           label = "More Chinese runners \n than Japan", 
           colour = bar_color,size =5.6, family = "Times")

asian_plot
```

## Americas

```{r}
# Colors
point_color <- "#BBD3FB"
bar_color <- "#333399"
  
# Labels
df_labels <- 
  runners_cont %>% 
  filter(continent == "Americas", nationality %in% c("USA", "CAN")) 

amer_plot <- 
  plot_cont(runners_cont, "Americas", point_color, bar_color) +
  labs(x = "", y = "") +
  annotate("text", x = 5,  y = 11000, 
           label = "From Americas", 
           colour = bar_color, size =7.0, family = "Georgia") +
  theme(axis.text.y = element_blank()) +
  
  geom_curve(aes(x = 8, y = 7604, xend = 9.2, yend = 7700),
               arrow = arrow(length = unit(0.35,"cm")), 
             color = point_color, size = 0.8, curvature = -0.3) +
  annotate("text", x = 9.7,  y = 7750, 
           label = "7604 \n Runners", 
           colour = bar_color,size =5.6, family = "Times")

amer_plot
```

## Europe

```{r}
# Colors
point_color <- "#A1DB7E"
bar_color <- "#008F7A"
  
# Labels
df_labels <- 
  runners_cont %>% 
  filter(continent == "Europe", nationality %in% c("FRA", "GBR")) 

euro_plot <- 
  plot_cont(runners_cont, "Europe", point_color, bar_color) +
  labs(x = "", y = "") +
  annotate("text", x = 5,  y = 11000, 
           label = "From Europe", 
           colour = bar_color, size =7.0, family = "Georgia") +
  theme(axis.text.y = element_blank()) +
  
  geom_curve(aes(x = 8, y = 4874, xend = 8.9, yend = 6450),
               arrow = arrow(length = unit(0.35,"cm")), 
             color = point_color, size = 0.8, curvature = -0.3) +
  annotate("text", x = 9.2,  y = 6850, 
           label = "4874 \n Runners", 
           colour = bar_color,size =5.6, family = "Times")

euro_plot
```

## Data checks

```{r}
runners_cont %>% 
  filter(nationality %in% c("FRA"), year == "2019")

runners_cont %>% 
  filter(nationality %in% c("USA"), year == "2019")

runners_cont %>% 
  filter(nationality %in% c("CHN"), year == "2019")

```

## Final Plot collage

```{r}
ggp_all <- (asian_plot + amer_plot + euro_plot) +    # Create grid of plots with title
  plot_annotation(title = "Ultra trail runners across continents", 
                  subtitle = "Labelled two countries per continent that has the highest trail runners.The other countries in the continent were colored black.", 
                  caption = "Tidy Tuesday 10-26-2021 Visualisation by: Kesava Asam \n Data source: BjnNowak-Github Repo") & 
  theme(plot.title = element_text(hjust = 0.5, size = 26, family = "Georgia"),
        plot.subtitle = element_text(hjust = 0.5, size = 16, family = "Georgia"), 
        plot.caption = element_text(hjust = 0.5, size = 10, family = "Georgia"))
ggp_all     
```


# Save

```{r eval=FALSE, include=FALSE}
ggsave("tidy_tuesday_ultra_trail_runners_plot_1029.jpeg", 
       plot = last_plot(), width = 600, height = 350, 
       units = "mm", dpi = 300)
```

# Session

```{r eval=FALSE, include=TRUE}
sessionInfo()
```


R version 4.1.1 (2021-08-10)
Platform: x86_64-apple-darwin17.0 (64-bit)
Running under: macOS Big Sur 11.6

Matrix products: default
LAPACK: /Library/Frameworks/R.framework/Versions/4.1/Resources/lib/libRlapack.dylib

locale:
[1] en_US.UTF-8/en_US.UTF-8/en_US.UTF-8/C/en_US.UTF-8/en_US.UTF-8

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base     

other attached packages:
 [1] countrycode_1.3.0  patchwork_1.1.1    scales_1.1.1       janitor_2.1.0      tidytuesdayR_1.0.1 forcats_0.5.1     
 [7] stringr_1.4.0      dplyr_1.0.7        purrr_0.3.4        readr_2.0.2        tidyr_1.1.4        tibble_3.1.5      
[13] ggplot2_3.3.5      tidyverse_1.3.1   

loaded via a namespace (and not attached):
 [1] tidyselect_1.1.1 xfun_0.26        haven_2.4.3      snakecase_0.11.0 colorspace_2.0-2 vctrs_0.3.8     
 [7] generics_0.1.0   usethis_2.0.1    utf8_1.2.2       rlang_0.4.11     pillar_1.6.3     glue_1.4.2      
[13] withr_2.4.2      DBI_1.1.1        bit64_4.0.5      dbplyr_2.1.1     modelr_0.1.8     readxl_1.3.1    
[19] lifecycle_1.0.1  munsell_0.5.0    gtable_0.3.0     cellranger_1.1.0 rvest_1.0.1      knitr_1.36      
[25] tzdb_0.1.2       parallel_4.1.1   curl_4.3.2       fansi_0.5.0      broom_0.7.9      Rcpp_1.0.7      
[31] backports_1.2.1  vroom_1.5.5      jsonlite_1.7.2   farver_2.1.0     bit_4.0.4        fs_1.5.0        
[37] digest_0.6.28    hms_1.1.1        stringi_1.7.5    grid_4.1.1       cli_3.0.1        tools_4.1.1     
[43] magrittr_2.0.1   crayon_1.4.1     pkgconfig_2.0.3  ellipsis_0.3.2   xml2_1.3.2       reprex_2.0.1    
[49] lubridate_1.7.10 assertthat_0.2.1 httr_1.4.2       rstudioapi_0.13  R6_2.5.1         compiler_4.1.1  
