---
title: 'Tidy Tuesday: Emmy Awards'
author: "Kesava Asam"
date: 'Report Last Run: `r Sys.time()`'
output:
  pdf_document:
    toc_depth: 2
    number_sections: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("~/Documents/tidytuesday/emmy_awards_09222021/")
```

\centering
\raggedright
\newpage
\tableofcontents

\newpage

# Packages

```{r}
# load required packages
library(tidyverse)
library(tidytuesdayR)

theme_set(theme_light())
```

# Data

```{r}
data_tue <- tidytuesdayR::tt_load('2021-09-21')
```

Emmy nominees and awards data

```{r}
emmy_nom <- data_tue$nominees
```

After checking the data and cleaning. My idea is to select Emmy Winners, separate the production column to get the Make up artists. Plot a graph of the number of winning makeup artists for the shows. 

Cleaning steps:

  - Recode SNL special and regular under one Title
  
  - Recode AHS all seasons under one Title
  
  - Recode Star Trek all seasons under one Title
  
  - Separate production to see names and title separate

\newpage

# Makeup Artists 

```{r}
makeup_emmy <- 
  emmy_nom %>% 
  filter(type == "Winner") %>% 
  group_by(category) %>% 
  separate(production, c("Name", "Profession"), 
           sep = ",", extra = "merge") %>% 
  filter(str_detect(Profession, 'Makeup')) %>% 
  mutate(title = recode(title, 
                        "The Saturday Night Live 40th Anniversary Special" = 
                          "The Saturday Night Live", 
                        "American Horror Story: Roanoke" = 
                          "American Horror Story", 
                        "American Horror Story: Hotel" = 
                          "American Horror Story",
                        "American Horror Story: Freak Show" = 
                          "American Horror Story", 
                        "Star Trek: Picard" = "Star Trek", 
                        "Star Trek: Discovery" = "Star Trek")) %>% 
  group_by(title) %>% 
  summarise("wins" = n()) %>% 
  arrange(desc(wins)) 
```

\newpage

```{r}
p1 <- 
  makeup_emmy %>% 
  head(11) %>% 
  ggplot() + 
  geom_hline(aes(yintercept = y), 
             data.frame(y = c(0:3) * 10),
             color = "gray50") + 
  geom_col(aes(x = reorder(str_wrap(title, 5), wins),
               y = wins, 
               fill = wins),
           position = "dodge2",
           show.legend = TRUE,
           alpha = 0.8) + 
  geom_point(aes(x = reorder(str_wrap(title, 5), wins),
                 y = wins),
             size = 2,
             color = "gray20") +
  geom_segment(aes(x = reorder(str_wrap(title, 5), wins),
                   y = 0,
                   xend = reorder(str_wrap(title, 5), wins),
                   yend = 35), linetype = "dashed",
               color = "gray10") + 
  coord_polar() 
```

## Add labels for scales

```{r}
p2 <- 
  p1 + 
  annotate(x = 11.55, y = 6, label = "5", geom = "text", color = "gray12", family = "serif") + 
  annotate(x = 11.55, y = 11, label = "10", geom = "text", color = "gray12", family = "serif") + 
  annotate(x = 11.55, y = 16, label = "15", geom = "text", color = "gray12", family = "serif") +
  annotate(x = 11.55, y = 21, label = "20", geom = "text", color = "gray12", family = "serif") +
  annotate(x = 11.55, y = 26, label = "25", geom = "text", color = "gray12", family = "serif") +
  annotate(x = 11.55, y = 31, label = "30", geom = "text", color = "gray12", family = "serif") +
  scale_y_continuous(limits = c(-5, 35), expand = c(0, 0),
    breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40)) 
```

\newpage

```{r fig.height=8, fig.width=8}
p2
```

\newpage

## Add colors 

```{r}
p3<- 
  p2 + 
  scale_fill_gradientn("No.of Wins",
     colours = c("#AA646B", "#F38F99", "#F4A999", "#F8E0B6", "#E4BD98", "#D69F7E", "#774936"),
     limits=c(5,35), breaks = c(5, 10, 15, 20, 25, 30, 35)) +
  theme(axis.title = element_blank(),
    axis.ticks = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_text(color = "gray15", size = 11),
    legend.position = "bottom", 
    text = element_text(color = "gray12", family = "Times")) 
```

## Add Labs

```{r}
final_plot <- 
  p3 +
  labs(title = "SNL has won most makeup artist Emmys", 
       subtitle = "Data range is from 2017 to 2021. Merged all AHS and Star Trek seasons into respective titles.", 
       caption = "TidyTuesday 2021-09-21. Visualisation by Kesava Asam.\n Data Source: Emmy") +
  theme(plot.title = element_text(face = "bold", size = 16, hjust = 0.01),
    plot.subtitle = element_text(size = 12, hjust = 0.05),
    plot.caption = element_text(size = 10, hjust = .5))
```

\newpage

```{r fig.height=10, fig.width=10}
final_plot
```


```{r eval=FALSE, include=FALSE}
ggsave("tidy_tuesday_emmys_result.png", 
       plot = last_plot(), width = 220, height = 220, 
       units = "mm", dpi = 400)
```

\newpage

# Reference

Thanks Tobias Stadler and Tomás Capretto for helping me generate the Circular barplot. [ref](https://www.r-graph-gallery.com/web-circular-barplot-with-R-and-ggplot2.html)
