---
title: 'Tidy Tuesday: Big Pumpkin'
author: "Kesava"
date: 'Report Last Run: `r Sys.time()`'
output:
  html_document:
    code_folding: hide
    theme: flatly
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

Install required packages

```{r message=FALSE, warning=FALSE}
# load required packages
library(tidyverse)
library(tidytuesdayR)
library(scales)
library(ggdark)
```

# Import Data

Get this weeks data from Tidy tuesday github.

```{r}
data_tue <- tt_load('2021-10-19', auth = github_pat())
```

# Check data

```{r}
data_tue$pumpkins %>% group_by(grower_name) %>% count() %>% arrange(desc(n))

data_tue$pumpkins %>% group_by(city) %>% count() %>% arrange(desc(n))

data_tue$pumpkins %>% arrange(desc(weight_lbs))
```

# Format data

```{r}
pumpkins <- 
  data_tue$pumpkins %>% 
  filter(!grepl("Entries",place)) %>% 
  unite("area", c(state_prov, country), sep = ", ", remove = F) %>% 
  mutate(city = stringr::str_to_title(city),
         weight_kgs = as.numeric(gsub(",", "", weight_lbs))/2.2046, 
         weight_metric_ton = weight_kgs/1000, 
         area = str_wrap(area, 25)) %>% 
  separate(id, c("year", "type"))
```

# Cleanup before plot

```{r}
# area order
area_ord <- pumpkins %>% 
  filter(weight_metric_ton > 1) %>% 
  arrange(desc(weight_kgs)) %>% 
  distinct(area) %>% 
  pull(area)

pumpkins %>%  
  filter(weight_metric_ton > 1) %>% 
  mutate(area = fct_relevel(area, area_ord)) %>% 
  select(area, weight_kgs, weight_lbs) %>% 
  arrange(desc(weight_kgs))
```

# Plot

```{r fig.height=14, fig.width=16}

pumpkins %>%  
  
  # Select required
  filter(weight_metric_ton > 1) %>% 
  
  # format
  mutate(area = fct_relevel(area, area_ord)) %>%
  
  # Plot
  ggplot(aes(weight_kgs, area)) +
  geom_segment(aes(y=area, yend = area, x= 950, xend=weight_kgs), 
               size = 1, color = "#63C328", alpha = 0.9) +
  geom_point(aes(size = weight_kgs), color = "#f2533f", alpha = 0.9)+
  scale_size_continuous(range = c(12,28)) +
  coord_cartesian(clip = 'off') +
  
  # Labels
  
  labs(y = "", 
       x = "", 
       title = "\n Distribution of Pumpkins that weigh more than a metric ton (1000 kg) \n", 
       caption = "\n Tidy Tuesday 10-19-2021 Visualisation by: Kesava Asam \n Data source: bigpumpkin.com") +
  
  # Scales
  
  scale_x_continuous(breaks = seq(0,1250, 50), 
                     limits = c(950, 1250), 
                     label = label_number(suffix = " kg", big.mark = "")) +
  
  
  # Theme settings
  
  dark_theme_minimal() +
  
  theme(legend.position = "none", 
        axis.text.y = element_text(size = 14, hjust = 1, color = "grey90"), 
        plot.title = element_text(color = "grey90", size = 26,
                                  family = "Georgia", hjust = 0.5), 
        plot.caption = element_text(hjust = 0.5)) +
  
  # Additional annotation
  
  geom_curve(aes(x = 1226, y = 1, xend = 1240, yend = 2.2),
               arrow = arrow(length = unit(0.35,"cm")), 
             color = "#BC82D6", linetype = "dashed", size = 0.8) +
  annotate("text", x = 1240,  y = 3, 
           label = "The Largest Pumpkin \n weighs 1226 kg or \n 2702 lbs.", 
           colour = "#E097FF",size =5.6, family = "Georgia") +
  
  
  geom_curve(aes(x = 1147, y = 5, xend = 1175, yend = 6.2),
               arrow = arrow(length = unit(0.35,"cm")), 
             color = "#BC82D6", linetype = "dashed", size = 0.8) +
  annotate("text", x = 1175,  y = 6.8, 
           label = "Largest Pumpkin in the US \n weighs 1147 kg or \n 2528 lbs.", 
           colour = "#E097FF",size =5.4, family = "Georgia")

```

# Save

```{r eval=FALSE, include=FALSE}
ggsave("tidy_tuesday_big_pumpkin_plot_1019.jpeg", 
       plot = last_plot(), width = 450, height = 400, 
       units = "mm", dpi = 300)
```

# Session

```{r eval=FALSE, include=TRUE}
sessionInfo()
```


R version 4.1.1 (2021-08-10)
Platform: x86_64-apple-darwin17.0 (64-bit)
Running under: macOS Big Sur 11.6

Matrix products: default
LAPACK: /Library/Frameworks/R.framework/Versions/4.1/Resources/lib/libRlapack.dylib

locale:
[1] en_US.UTF-8/en_US.UTF-8/en_US.UTF-8/C/en_US.UTF-8/en_US.UTF-8

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base     

other attached packages:
 [1] ggdark_0.2.1       scales_1.1.1       tidytuesdayR_1.0.1
 [4] forcats_0.5.1      stringr_1.4.0      dplyr_1.0.7       
 [7] purrr_0.3.4        readr_2.0.2        tidyr_1.1.4       
[10] tibble_3.1.5       ggplot2_3.3.5      tidyverse_1.3.1   

loaded via a namespace (and not attached):
 [1] tidyselect_1.1.1 xfun_0.26        haven_2.4.3      colorspace_2.0-2
 [5] vctrs_0.3.8      generics_0.1.0   usethis_2.0.1    utf8_1.2.2      
 [9] rlang_0.4.11     pillar_1.6.3     glue_1.4.2       withr_2.4.2     
[13] DBI_1.1.1        selectr_0.4-2    bit64_4.0.5      dbplyr_2.1.1    
[17] modelr_0.1.8     readxl_1.3.1     lifecycle_1.0.1  munsell_0.5.0   
[21] gtable_0.3.0     cellranger_1.1.0 rvest_1.0.1      knitr_1.36      
[25] tzdb_0.1.2       parallel_4.1.1   curl_4.3.2       fansi_0.5.0     
[29] broom_0.7.9      Rcpp_1.0.7       backports_1.2.1  vroom_1.5.5     
[33] jsonlite_1.7.2   farver_2.1.0     bit_4.0.4        fs_1.5.0        
[37] digest_0.6.28    hms_1.1.1        stringi_1.7.5    grid_4.1.1      
[41] cli_3.0.1        tools_4.1.1      magrittr_2.0.1   crayon_1.4.1    
[45] pkgconfig_2.0.3  ellipsis_0.3.2   xml2_1.3.2       reprex_2.0.1    
[49] lubridate_1.7.10 assertthat_0.2.1 httr_1.4.2       rstudioapi_0.13 
[53] R6_2.5.1         compiler_4.1.1 
