---
title: 'Tidy Tuesday: NBER Publication Data'
author: "Kesava Asam"
date: 'Report Last Run: `r Sys.time()`'
output:
  pdf_document:
    toc_depth: 2
    number_sections: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("~/Documents/tidy_tuesday/nber_publication")
```

\centering
\raggedright
\newpage
\tableofcontents

\newpage

# Packages

```{r}
# load required packages
library(tidyverse)
library(tidytuesdayR)
library(ggdark)
theme_set(theme_light())
```

# Data

```{r}
# read in the data manually
papers <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-09-28/papers.csv')
programs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-09-28/programs.csv')
paper_programs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-09-28/paper_programs.csv')
```

NBR Publication data

Data set for graphs

```{r}
pub_data <- 
  inner_join(papers, paper_programs) %>% 
  inner_join(programs) 
```

Check the data

```{r}
pub_data %>% 
  count(year) %>% filter(year != 2021) %>% # 2021 is not complete
  ggplot(aes(x = year, y = n)) +
  geom_line()
```

Check recent 10 years per month submissions?

```{r}
pub_data %>% 
  count(year) %>% filter(year > 2009 & year != 2021) %>% 
  ggplot(aes(x = year, y = n)) +
  geom_line()
```

\newpage

# Function

Make a function to pick keywords

```{r}
pick_title <- function(term_int) {
  
  pub_data %>%  
    filter(year != 2021 & year > 1989) %>% 
    distinct(title, .keep_all = T) %>% 
    filter(grepl({{term_int}}, title)) %>% 
    group_by(year) %>% 
    mutate(count = n()) %>% 
    ungroup()
}
```

\newpage

# Subset

## Sex related

```{r}
sex_df <- 
  pick_title('Gender|Sex |Male|Female|Girls|Boys|Women|Men ') %>% 
  mutate('category' = "Gender")
```

## Health related

```{r}
health_df <- 
  pick_title('Health|fitness') %>% 
  mutate('category' = "Health")
```

## Retirement

```{r}
retire_df <- 
  pick_title('Retirement') %>% 
  mutate('category' = "Retirement")
```


## Education

```{r}
edu_df <- 
  pick_title('Education|University|School') %>% 
  mutate('category' = "Education")
```

# Defense

```{r}
def_df <- 
  pick_title('Defense|Army|Military|Navy') %>% 
  mutate('category' = "Defense")
```

# Pollution

```{r}
poll_df <- 
  pick_title('Pollution|Climate|Recycling|Hazardous') %>% 
  mutate('category' = "Pollution/Climate")
```

## Combine

```{r}
df_cat_int <- rbind(health_df, edu_df, retire_df, 
                  sex_df, def_df, poll_df) 
```

\newpage

# Visualization

```{r}
# Custom colors
colrs_1 <- c("#E83122", "#FAA42E", "#FAEB36", "#82CA20", "#487DE7", "#4B369D")
colrs_2 <- c('#E12D7B','#F67B52', "#EDCD3B", "#3BBC54", "#2665BD", "#481899")

# Plot
p <- df_cat_int %>% 
  ggplot(aes(x = year, y = count, color = category, fill = category)) +
  geom_line(alpha = 0.20) +
  geom_smooth(method = 'loess', formula = 'y ~ x')+
  scale_color_manual(values=colrs_2)+
  scale_fill_manual(values=colrs_1)+
  scale_x_continuous(breaks = seq(1990, 2020, 2)) +
  scale_y_continuous(breaks = seq(0, 70, 5)) +
  labs(title = "Health and Education terms have signifcantly increased in NBER Publications over time!",
    subtitle= "Words seen in the National Bureau of Economic Research papers' titles from 1990 to 2020.Smoothing method used is 'loess'.", 
    caption = "TidyTuesday 2021-09-28. Visualisation by Kesava Asam.\n Data Source:NBER by Bern Davis",
       x= "", y = "Number of papers", 
       fill = "Word Related to", 
       color = "Word Related to") 
```

```{r fig.height=8, fig.width=12}
# Using the dark_mode from ggdark by nsgrantham
p + dark_mode() +
  theme(legend.position = "bottom")
```


```{r eval=FALSE, include=FALSE}
ggsave("tidy_tuesday_nber_publications_result.png", 
       plot = last_plot(), width = 250, height = 200, 
       units = "mm", dpi = 300)
```

\newpage

# References:
      - [Color palletes](https://www.schemecolor.com/kaleidoscope-rainbow.php)
      - [GGDark](https://github.com/nsgrantham/ggdark)   





```{r}
sessionInfo()
```

